---
output: github_document
---

# README

[![Travis build status](https://travis-ci.org/SCCWRP/SQObioaccumulation.svg?branch=master)](https://travis-ci.org/SCCWRP/SQObioaccumulation)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/SCCWRP/SQObioaccumulation?branch=master&svg=true)](https://ci.appveyor.com/project/SCCWRP/SQObioaccumulation)

```{r setup, message = F, warning = F, echo = F}
library(knitr)
opts_chunk$set(message = F, warning = F)
```


Install the package as follows:

```{r, eval = F}
install.packages('devtools')
library(devtools)
install_github('SCCWRP/SQObioaccumulation')
library(SQObioaccumulation)
```
```{r, message = F, echo = F}
devtools::load_all()
```

Run the bioaccumulation model with defaults:

```{r}
# data inputs
data(biota)
data(constants)
data(contam)
data(biota_preyprop)

# calculated contaminant inputs
contamcalc <- cntcalc(contam, constants)

# run model
res <- bioaccum_batch(biota, contamcalc, biota_preyprop, constants)

# assign output to separate objects
cbiota <- res$cbiota
bsaf <- res$bsaf
```

Creat a summary table:

```{r}
# summary table
indic_sum <- indic_sum_fun(cbiota, contamcalc)
indic_sum
```

Plot BSAF and tissue concentration estimates for a selected contaminant:

```{r, fig.height = 7, fig.width = 9}
# plot of bsaf, cbiota by specific contaminant
plo_bsaf(bsaf, cbiota, 'alphaChlordane')
```

Make a table of BSAF and tissue concentration estimates for a selected contaminant:

```{r}
# tabular summary of bsaf, cbiota by specific contaminant
tab_bsaf(bsaf, cbiota, 'alphaChlordane')
```

Run Monte Carlo simulations (MCS) with results from bioaccumulation model and additional inputs:

```{r}
mcsres <- mcs_fun(1000, indic_sum, mcsparms, constants)
```

Summarize MCS results:

```{r}
mcs_sum_fun(mcsres)
```

Plot cumulative distribution curves for MCS: 

```{r, fig.height = 7, fig.width = 8, out.width = '80%', fig.align = 'center', warning = F}
mcs_plo(mcsres, xmax = 3)
```

Get overall SQO assessment:

```{r}
wgtavg <- wgt_avg_fun(mcsparms)
sqo_sum_fun(wgtavg, mcsres, tischmthr, constants, finalsiteassess)
```



